Agile Inter-team Software Development

### 2019-01-20 Draft/Parts/Main.tex
Added Parnas72 (cite + text).

>>>>

In addition to specification of system elements, architecture can also be used to empower teams.
As discussed by Parnas \cite{Parnas72}, there are two general approaches to decomposing systems: 1) compartmentalizing a computational process and, 2) focusing on information hiding.
The latter approach ideal for agile development since this approaches defines system components in terms of design dicisions, which empowers invidual teams.
